Inferring stellar rotation periods using Gaussian processes

### 2017-01-31 documents/ms.tex
small changes to text

\item The flexibility of this GP model allows for insidious kinds of
posterior multimodality and ``over-fitting''--like behavior.  For example,
if $l$ is small,  the non-periodic factor in the covariance kernel may
dominate, allowing for a good fit to the data without requiring any
periodic covariance structure---even if
clear periodic structure is present.  Additionally, if $\Gamma$ is too large,
then [explain in more technical terms that ``the GP gets way too wiggly and
overfits the data without caring about the periodicity.'' ]

\item In some cases, the posterior may also be multi-modal in period---that is,
there may be significant posterior density at half or twice the true period $P$.
This is related to how the ACF method must guard against identifying periods
at half or twice the true period.
\end{itemize}

@@

In order to manage the great flexibilty of the GP model and focus on
reliably retrieving the period parameter, we also impose priors
on the non-period GP parameters that we
learned during the development of this method.
Beginning with very broad priors (uniform in log space between
-20 and 20) on all the parameters, we first explored what the
typical values of the non-period parameters tended to be when the
injected periods were successfully recovered.  We also experimented with
constraining the allowed ranges of the parameters, after discovering
that some regions of parameter space (such as large values of $A$ and $\Gamma$
and small values of $l$) tended to allow fits that ignored the desired
periodicity.  The priors and bounds we used for this work are listed in
table \ref{tab:priors}.  We note that we do not have any specific
quantitative justification for the use of these priors,
except that they produce good results for this particular test set of
light curves.  We thus caution that other data sets might have different
noise properties, potentially requiring modifications to these priors
on the non-period parameters (e.g., see Section \ref{sec:kepler}).  
For period, we tried two different methods:
an uninformed (log-flat) prior between 0.5\,d and 100\,d, and an ACF-informed
prior (details in Appendix.)
% We note that our default prior for period is
% log-uniform between the bounds, but that we were also able to
% further improve our results by using an ACF-inspired prior.

>>>>

\item The flexibility of this GP model allows for posterior multimodality and
``over-fitting''--like behavior.
For example, if $l$ is small,  the non-periodic factor in the covariance
        kernel may dominate, allowing for a good fit to the data without
        requiring any periodic covariance structure---even if clear periodic
        structure is present.
Additionally, if $\Gamma$ is too large, the GP model becomes extremely
        flexible and can fit the data without varying the period.

\item In some cases, the posterior may also be multi-modal in period---that is,
there may be significant posterior density at half or twice the true period $P$.
\end{itemize}

@@

In order to manage the flexibilty of the GP model and focus on reliably
retrieving the period parameter, we also impose priors on the non-period GP
parameters, learned during the development of this method.
Beginning with very broad priors (uniform in log space between -20 and 20) on
all the parameters, we first explored the typical values of the non-period
parameters when the injected periods were successfully recovered.
We also experimented with constraining the allowed ranges of the parameters
after discovering that some regions of parameter space (such as large values
of $A$ and $\Gamma$ and small values of $l$) tended to allow fits that ignored
the desired periodicity.
The priors and bounds we used for this work are listed in table
\ref{tab:priors}.
We note that we do not have any specific quantitative justification for the
use of these priors, except that they produce good results for this particular
test set of light curves.
We thus caution that other data sets might have different noise properties,
potentially requiring modifications to these priors on the non-period
parameters (e.g., see Section \ref{sec:kepler}).
For the period prior, we tried two different methods: an uninformed (log-flat)
prior between 0.5\,d and 100\,d, and an ACF-informed prior (details in
Appendix.)
% We note that our default prior for period is log-uniform between the bounds,
% but that we were also able to further improve our results by using an
% ACF-inspired prior.
